### 2025-03-09 chapters/introduction.tex
Changes 1. Added more figures for introduction and literature review 2. Completed introduction and lit review for draft 1 3. Added figures for Aim 3 section

\begin{figure}[h]
    \centering
    \includegraphics[scale = 2]{figures/literature_review/STRIPPS.jpg}
    \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
    the casting mixture through diffusion. Reproduced from Haase et al. 2015 under license number 5913140219015. \cite{haase_continuous_2015}}
    \label{fig:strips}
\end{figure}

@@

\textcolor{blue}{ADD IN PICTURE FROM THAM 2021 AND CUI 2013 ON EXAMPLES OF STIMULI RESPONSE IN EMULSIONS}

Stimuli-responsive mechanisms based on pH, external fields, and temperature have been explored in previous studies to modify the microstructure of emulsion 
droplets for applications such as enhanced oil recovery, pharmaceuticals, and cell adhesion 
\cite{haase_nanoparticle_2011, tham_magnetophoresis_2021, cui_stabilizing_2013, manfredini_limonene--water_2021}. External fields have been shown to 
manipulate emulsion stability, control droplet movement, and induce elongation in emulsion droplets 
\cite{tham_magnetophoresis_2021, cui_stabilizing_2013, melle_pickering_2005}.  
In the case of bijels, spherical particle-stabilized systems subjected to a magnetic field exhibited no significant microstructural changes 
\cite{kim_bijels_2010}. However, bijels stabilized with spherical particles under an electric field demonstrated greater potential for microstructure 
modification \cite{carmack_tuning_2018}. Despite this, magnetic fields present a promising avenue for targeted stimuli-responsive behavior, as even 
weak fields can induce a response while remaining non-invasive in many contexts. This property is particularly advantageous for pharmaceutical and 
bioengineering applications, where external control over material properties is desirable 
\cite{vanoli_bijels_2022, thorson_bijel-templated_2019, thorson_composite_2018}.  
Such applications could benefit from in-situ microstructural modifications, enabling tunable drug delivery rates, improved separations, and enhanced catalyst 
efficiency and permeability. Therefore, developing strategies to modify pore size and tortuosity without requiring the synthesis of a new material would 
significantly expand the functional versatility of bijels.

Anisotropic particles at interfaces have been shown to undergo self-assembly due to the presence of multipolar pressure fields induced by interface 
deformation. Similarly, self-assembly has been observed for ellipsoidal particles at interfaces under magnetic fields. Additionally, ellipsoidal particles 
exhibit magnetic field-controlled orientation at interfaces, as demonstrated by Bresme and Faraudo \cite{bresme_orientational_2007, davies_interface_2014}.  
When subjected to a magnetic field, assemblies of multiple ellipsoidal particles exhibit energy minima at orientations different from those of isolated 
particles. This suggests that the interfacial coverage of surfaces decorated with ellipsoidal particles can be dynamically tuned using external 
stimuli \cite{newton_influence_2014, newton_capillary_2018}. Therefore, ellipsoidal particles at interfaces—whose orientation and packing can be externally 
controlled—present a promising strategy for tailoring the microstructure of bijels.

@@

In many of the fabrication processes described above, the rheology of the bijel casting mixture plays a crucial role 
\cite{haase_continuous_2015, cai_bijels_2017, amirfattahi_fabrication_2024}. Ching demonstrated that, rheologically, bijels behave as colloidal 
glasses percolating in 3D space \cite{ching_bijel_2022}. A shear capillary number, \( Ca_s \), is defined to correlate the applied strain rate 
with the capillary forces derived from surface tension \cite{frijters_effects_2012, yang_capillary_2022}. This study aims to identify the effect 
of the initial microstructure and applied field on the rheological properties of the bijel.

@@

In this study, the yield stress and viscosity of the bijels will be examined as a function of the initial microstructure under various $Ca_s$ values. 
The initial microstructure will be derived from bijels stabilized with ellipsoidal particles, synthesized both without a magnetic field and with a field 
strength equal to the surface tension energy. Constant shear, defined by $Ca_s$, will be applied to determine the yield stress and non-Newtonian 
characteristics of the bijel. Previous studies have shown that particle ordering in the direction of shear significantly alters the rheological behavior 
compared to unordered systems. Additionally, the domains within the bijel may introduce new mechanisms for modifying rheological properties, which have 
yet to be explored in detail.

We will then investigate the complex rheology of the bijels by calculating the loss and storage moduli of the bijel microstructures described 
earlier as a function of oscillatory shear. The loss and storage moduli describe the viscous and elastic behavior of the bijel, respectively, 
allowing the gel point of the bijel to be determined as the point at which the storage modulus exceeds the loss modulus. Special attention will be 
given to the state of the particles in all simulations, correlating changes in particle properties with observed rheological events. Additionally, 
we will assess whether shear banding occurs.

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[scale = 4]{figures/introduction/STrIPS.jpg}
    \caption{STrIPS in action. Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
    the casting mixture through diffusion. Reproduced from Haase et al. 2015 under license number 5913140219015. \cite{haase_continuous_2015}}
    \label{fig:strips}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale = 1]{figures/introduction/magnetophoresis_emulsion.jpeg}
    \caption{Enhanced oil recovery of oil from water using magnetically responsive emulsion stabilizers, allowing for 
             locomotion and controlled coalescence of cargo from a matrix phase using magnetic fields relevant in 
             water filtration and oil refining applications. Reproduced from Tham et al. 2021 under the ACS standard license \cite{tham_magnetophoresis_2021}}
    \label{fig:magnetophoresis_droplet}
\end{figure}

Stimuli-responsive mechanisms based on pH, external fields, and temperature have been explored in previous studies to modify the microstructure of emulsion 
droplets for applications such as enhanced oil recovery, pharmaceuticals, and cell adhesion 
\cite{haase_nanoparticle_2011, tham_magnetophoresis_2021, cui_stabilizing_2013, manfredini_limonene--water_2021}. External fields have been shown to 
manipulate emulsion stability, control droplet movement, and induce elongation in emulsion droplets 
\cite{tham_magnetophoresis_2021, cui_stabilizing_2013, melle_pickering_2005}. One such example is shown in Figure \ref{fig:magnetophoresis_droplet}
where enhanced oil recovery was performed using magnetically responsive particle stabilizers which could capture oil droplets,
move the droplets away from the matrix and cause controlled coalescence elsewhere.
In the case of bijels, spherical particle-stabilized systems subjected to a magnetic field exhibited no significant microstructural changes 
\cite{kim_bijels_2010}. However, bijels stabilized with spherical particles under an electric field demonstrated greater potential for microstructure 
modification \cite{carmack_tuning_2018}. Despite this, magnetic fields present a promising avenue for targeted stimuli-responsive behavior, as even 
weak fields can induce a response while remaining non-invasive in many contexts. This property is particularly advantageous for pharmaceutical and 
bioengineering applications, where external control over material properties is desirable 
\cite{vanoli_bijels_2022, thorson_bijel-templated_2019, thorson_composite_2018}.  
Such applications could benefit from in-situ microstructural modifications, enabling tunable drug delivery rates, improved separations, and enhanced catalyst 
efficiency and permeability. Therefore, developing strategies to modify pore size and tortuosity without requiring the synthesis of a new material would 
significantly expand the functional versatility of bijels.

\begin{figure}[h]
    \centering
    \includegraphics[scale = 0.4]{figures/introduction/anisotropic_particles_assembly.jpg}
    \caption{Assembly of prolate particles on a flat interface at various interfacial coverages and field strengths,
             showing the self assembly into chains that ellipsoidal particles can undergo under applied magnetic fields at
             interfaces. Reproduced from Davies et al. under the Creative Commons CC BY license \cite{davies_assembling_2014}}
    \label{fig:anisotropic_assembly}
\end{figure}

Anisotropic particles at interfaces have been shown to undergo self-assembly due to the presence of multipolar pressure fields induced by interface 
deformation caused by magnetic stimuli, visualized in Figure \ref{fig:anisotropic_assembly}. \cite{bresme_orientational_2007, davies_interface_2014}
When subjected to a magnetic field, assemblies of multiple ellipsoidal particles exhibit energy minima at orientations different from those of isolated 
particles. This suggests that the interfacial coverage of surfaces decorated with ellipsoidal particles can be dynamically tuned using external 
stimuli \cite{newton_influence_2014, newton_capillary_2018}. Therefore, ellipsoidal particles at interfaces—whose orientation and packing can be externally 
controlled—present a promising strategy for tailoring the microstructure of bijels.

@@

In many of the fabrication processes described above, the rheology of the bijel casting mixture plays a crucial role 
\cite{haase_continuous_2015, cai_bijels_2017, amirfattahi_fabrication_2024}. Furthermore, the mechanical performance of the
resulting bijel is a key constraint for bijels in cross flow reactors or water filtration applications. \cite{boakye-ansah_controlling_2020}
Under high shear, the bijel can fail due to particles being ejected from the interface limiting the flow rate and pressure that can
be used when using bijels as cross flow reactors or water filtration systems. Ching demonstrated that, rheologically, bijels behave 
as colloidal glasses percolating in 3D space \cite{ching_bijel_2022}. This implies a yield stress above which flow of the material
will initiate. Bijels are also shear thinning as fluid-particle interactions increase the effective viscosity at lower shear rates.

@@

In this study, the yield stress and viscosity of the bijels will be examined as a function of the initial microstructure under various $Ca_s$ values. 
A shear capillary number, $Ca_s$, is defined to correlate the applied strain rate with the capillary forces derived from surface tension 
\cite{frijters_effects_2012, yang_capillary_2022}. This study aims to identify the effect 
of the initial microstructure and applied field on the rheological properties of the bijel.The initial microstructure will be 
derived from bijels stabilized with ellipsoidal particles, synthesized both without a magnetic field and with a field 
strength equal to the surface tension energy. Constant shear, defined by $Ca_s$, will be applied to determine the yield stress and non-Newtonian 
characteristics of the bijel. Previous studies have shown that particle ordering in the direction of shear significantly alters the rheological behavior 
compared to unordered systems. Additionally, the domains within the bijel may introduce new mechanisms for modifying rheological properties, which have 
yet to be explored in detail.

% We will then investigate the complex rheology of the bijels by calculating the loss and storage moduli of the bijel microstructures described 
% earlier as a function of oscillatory shear. The loss and storage moduli describe the viscous and elastic behavior of the bijel, respectively, 
% allowing the gel point of the bijel to be determined as the point at which the storage modulus exceeds the loss modulus. Special attention will be 
% given to the state of the particles in all simulations, correlating changes in particle properties with observed rheological events. Additionally, 
% we will assess whether shear banding occurs.

### 2025-03-09 chapters/lit_review.tex
Changes 1. Added more figures for introduction and literature review 2. Completed introduction and lit review for draft 1 3. Added figures for Aim 3 section

The existence of particle-stabilized emulsions has been recognized for over a century, following the independent discoveries by Pickering and Ramsden, who observed dispersed 
oil droplets within a water matrix after vigorous stirring of an oil-water-particle mixture \cite{ramsden_separation_1904, pickering_cxcvi.emulsions_1907}. Unlike surfactants, 
which stabilize emulsions by reducing interfacial tension, particles act as stabilizers by adsorbing at the interface between the dispersed and continuous phases, thereby 
preventing direct contact between them. The Pieranski model, derived from \textcolor{blue}{insert derivation of Pieranski model}, is commonly used to determine the adsorption 
energy of a particle at an interface. It is expressed as $ G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2 $ where $G_{ads}$ represents the free energy reduction upon particle 
adsorption, $\sigma$ is the surface tension between the partially miscible fluids, and $ \theta_c $ is the contact angle of the particle. Particles at the interface are 
generally considered irreversibly adsorbed, even at the nanoscale. For particles larger than 100 nm, the adsorption energy is sufficiently high that thermal fluctuations at 
the interface can be considered negligible \cite{cheung_molecular_2011}.

@@

Bijels were first synthesized using Thermally Induced Phase Separation (TIPS) \cite{herzig_bicontinuous_2007, lee_bicontinuous_2010, bai_dynamics_2015}. 
The process begins by identifying a small-molecule or polymer blend with a critical point, referred to as the casting mixture, and preparing it at a composition 
corresponding to this critical point. The casting mixture is then combined with particle surfactants while remaining in a single-phase state. Once the particles 
are homogeneously distributed, phase separation is induced by adjusting the temperature to bring the system into the two-phase region. By ensuring that the 
composition aligns with the critical point, the casting mixture undergoes spinodal decomposition, preventing nucleation and growth.

@@

\textcolor{blue}{Description of VIPS}

@@

\textcolor{blue}{Description of homogenization}

@@

\textcolor{blue}{Description of liquid in liquid printing}

Enter something about this method. \cite{amirfattahi_fabrication_2024}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 2]{figures/literature_review/bijel_under_shear.jpeg}
    \caption{Schematic of a bijel with hard-sphere particles undergoing shear, demonstrating migration and detachment of particles at the interface. 
    \cite{bonaccorso_shear_2020}}
    \label{fig:bijel_under_shear}
\end{figure}

@@

\section{Stimuli response in particle stabilized emulsions}

Kim et al. found that strong magnetic fields do not significantly alter the microstructure of a bijel stabilized with spherical particles, as the particles orient 
to the field without affecting interface ordering. \cite{kim_bijels_2010} In contrast, Carmack and Millet demonstrated that polarizable fluids and particles under 
an electric field show significant microstructural changes, with particles self-assembling into chains and forming cylindrical domains parallel to the applied field, 
thus modifying the microstructure. \cite{carmack_tuning_2018}

@@

In addition to the Shan-Chen model, the color gradient model, free energy model and interface tracking technique all 
allow for simulations of various types of multiphase and/or multicomponent flows. The color gradient model proposed by Rothman and Keller and 
implemented by Gunstensen et al relies upon modelling two particle distributions. These represent a binary fluid mixture with the collision step 
able to recover the hydrodynamics and non-ideal mixing dynamics. The free energy model utilizes phase field theory and constructs a free energy 
functional to recover interfacial dynamics and effects in a thermodynamically consistent manner. Often, a square gradient free energy is used for 
simplicity and ease of implementation. The mean field theory

The non-ideal mixing dynamics are recovered during the "recoloring" step, of which the technique proposed by Latva-Kokko and Rothman is more commonly 
used for soft matter flows. \cite{liu_multiphase_2016}

>>>>

The existence of particle-stabilized emulsions has been recognized for over a century, following the independent discoveries by Pickering and Ramsden, who observed dispersed 
oil droplets within a water matrix after vigorous stirring of an oil-water-particle mixture \cite{ramsden_separation_1904, pickering_cxcvi.emulsions_1907}. Unlike surfactants, 
which stabilize emulsions by reducing interfacial tension, particles act as stabilizers by adsorbing at the interface between the dispersed and continuous phases, thereby 
preventing direct contact between them. The Pieranski model is commonly used to determine the adsorption 
energy of a particle at an interface. It is expressed as $ G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2 $ where $G_{ads}$ represents the free energy reduction upon particle 
adsorption, $\sigma$ is the surface tension between the partially miscible fluids, and $ \theta_c $ is the contact angle of the particle. Particles at the interface are 
generally considered irreversibly adsorbed, even at the nanoscale. For particles larger than 100 nm, the adsorption energy is sufficiently high that thermal fluctuations at 
the interface can be considered negligible \cite{cheung_molecular_2011}.

@@

The existence of bijels was first identified computationally using a multicomponent lattice boltzmann method which looked at 
the jamming of spherical particles in a binary fluid system with equal volume fraction of each fluid. 
\cite{stratford_colloidal_2005} Once phase separation was initiated, the particles adsorb onto the interface until the interfacial
area matches the cross sectional area of the particles at the interface, when domain coarsening is ceased. The simulation assumed
an equal volume fraction of fluid components and neutrally wetting particles to not impart preferential curvature onto the interface.
Figure \ref{fig:state_diagram_particle_emulsions} demonstrates a schematic derived from experimental results of particle stabilized
emulsion microstructures that form when changing the volume fraction and particle contact angle.

In experiments, bijels were first synthesized using Thermally Induced Phase Separation (TIPS) \cite{herzig_bicontinuous_2007, lee_bicontinuous_2010, bai_dynamics_2015}. 
The process begins by identifying a small-molecule or polymer blend with a critical point, referred to as the casting mixture, and preparing it at a composition 
corresponding to this critical point. The casting mixture is then combined with particle surfactants while remaining in a single-phase state. Once the particles 
are homogeneously distributed, phase separation is induced by adjusting the temperature to bring the system into the two-phase region. By ensuring that the 
composition aligns with the critical point, the casting mixture undergoes spinodal decomposition, preventing nucleation and growth.

\begin{figure}
    \centering
    \includegraphics[scale = 0.2]{figures/literature_review/state_diagram.jpg}
    \caption{Formation criteria for a particle stabilized emulsion that can form bijel. 
            Reproduced from Velankar 2015 using license number 1551968-1. \cite{velankar_non-equilibrium_2015}}
    \label{fig:state_diagram_particle_emulsions}
\end{figure}

@@

@@

@@

% \textcolor{blue}{Description of liquid in liquid printing}

% Enter something about this method. \cite{amirfattahi_fabrication_2024}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 2]{figures/literature_review/bijel_under_shear.jpeg}
    \caption{Schematic of a bijel with hard-sphere particles undergoing shear, demonstrating migration and detachment of particles at the interface. 
             Reproduced from Bonaccorso et al. under the Creative Commons CC BY License. \cite{bonaccorso_shear_2020}}
    \label{fig:bijel_under_shear}
\end{figure}

@@

\section{Microstructure control in bijels}

Kim et al. used a free energy based lattice boltzmann method coupled with particles and magnetic fields to investigate the influence of magnetic fields on 
the microstructure of bijels stabilized with spherical particles. \cite{kim_bijels_2010}
They observed that applying strong magnetic fields did not significantly alter the bijel microstructure, as the particles aligned with 
the field without disrupting the interfacial ordering. This finding suggests that spherical particles, due to their isotropic shape, do 
not induce anisotropic stresses on the interface when subjected to magnetic fields, thereby maintaining the structural integrity of the bijel.

In contrast to the minimal impact of magnetic fields on bijels stabilized with spherical particles, Carmack and Millett investigated the effects of 
applied electric fields on thin-film bijels using a Cahn-Hilliard coupled with Langevin dynamics computational model. \cite{carmack_tuning_2018} 
Their study revealed that electric fields can induce significant microstructural changes in bijels, with particles self-assembling into chains and forming 
cylindrical domains aligned parallel to the applied field, thereby modifying the overall microstructure. Carmack and Millet observed that the dielectric contrast 
between liquid domains governs liquid domain alignment, and the dielectric contrast between colloidal particles and the liquid matrix induces dipolar particle 
interactions. By changing the dielectric contrast between particle and fluid, different bijel morphologies could be formed. Additionally, particle chains were found to 
act as nucleation sites for phase separation, influencing the resultant morphologies in terms of particle attachment to phase interface regions and average 
channel diameter.

While not strictly stimuli-responsive, microstructure modifications have been achieved by applying a particle volume fraction gradient during the formation of 
bijels using Thermally Induced Phase Separation (TIPS). \cite{french_bicontinuous_2022} In their study, French et al. allowed particles to partially sediment in the bijel casting mixture
before initiating thermal quenching. The gradient in particle volume fraction along the height of the reaction vessel caused the jamming point of the bijel
to vary along the gradient axis, causing a channel size gradients of up to 2.8\% per millimeter, as measured using confocal microscopy.

@@

In addition to the Shan-Chen model, the color gradient model, free energy model and interface tracking technique all 
allow for simulations of various types of multiphase and/or multicomponent flows. The color gradient model proposed by Rothman and Keller and 
implemented by Gunstensen et al relies upon modelling two particle distributions. These represent a binary fluid mixture with the collision step 
able to recover the hydrodynamics and non-ideal mixing dynamics. The free energy model utilizes phase field theory and constructs a free energy 
functional to recover interfacial dynamics and effects in a thermodynamically consistent manner. Often, a square gradient free energy is used for 
simplicity and ease of implementation. The mean field theory The non-ideal mixing dynamics are recovered during the "recoloring" step, of which the 
technique proposed by Latva-Kokko and Rothman is more commonly used for soft matter flows. \cite{liu_multiphase_2016}

### 2025-03-09 licenses/licenses.tex
Changes 1. Made tex files human readable again 2. Added content to paper3 tex file 3. Added licenses to some of the images from other papers
Changes 1. Added more figures for introduction and literature review 2. Completed introduction and lit review for draft 1 3. Added figures for Aim 3 section

\begin{itemize}
    \item Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, 
    Fibers, and Membranes by Solvent Transfer‐Induced Phase Separation (STRIPS): 5913140219015
    \item Scalable synthesis of gyroid-inspired freestanding three-dimensional graphene architectures: 1548092-1
    \item State diagram for particle stabilized emulsions. [Soft Matter, 2015,11, 8393-8403]: 1551968-1
    \item Scalable Manufacturing of Hierarchical Biphasic Bicontinuous Structures via Vaporization-Induced 
    Phase Separation (VIPS) [Materials Letters 2020, 2, 5, 524-530]: "Reprinted (adapted) with permission from 
    {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
    \item Modulation of Cellulose Nanocrystals Amphiphilic Properties to Stabilize Oil/Water Interface 
    [Biomacromolecules 2016, 17, 5, 1748–1756]: "Reprinted (adapted) with permission from 
    {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
    \item Dextran-Based Nanoparticles to Formulate pH-Responsive Pickering Emulsions: A Fully Degradable 
    Vector at a Day Scale [Biomacromolecules 2020, 21, 12, 5358–5368]: "Reprinted (adapted) with permission from 
    {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
    \item Stable emulsions with thermally responsive microstructure and rheology using poly(ethylene oxide) star 
    polymers as emulsifiers [Journal of Colloid and Interface Science, 2013, 394, 284-292]: 5921030909190
    \item Magnetophoresis of Magnetic Pickering Emulsions Under Low Field Gradient: Macroscopic and Microscopic 
    Motion [Langmuir 2021, 37, 5, 1811–1822]: "Reprinted (adapted) with permission from 
    {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
    \item Influence of magnetic field on the orientation of anisotropic magnetic particles at liquid interfaces 
    [Phys Chem Chem Phys 2014, 16, 47, 26051-26058]: 1551970-1
    \item Pickering Emulsions with Controllable Stability [Langmuir, 2005, 21, 6, 2158-2162]: "Reprinted (adapted) with permission from 
    {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
    \item Bijels Containing Magnetic Particles: A Simulation Study [Langmuir, 2010, 26, 11, 7928-7936]: 
    "Reprinted (adapted) with permission from {COMPLETE REFERENCE CITATION}. Copyright {YEAR} 
    American Chemical Society."
    \item Numerical simulations of particulate suspensions via a discretized Boltzmann equation. Part 2. Numerical results
    \item Aerobijels: Ultralight Carbon Monoliths from Cocontinuous Emulsions 
    [Adv. Funct. Mater. 2020, 30, 1908383]: 5921080017718
    \item Hierarchical assemblies of superparamagnetic colloids in 
    time-varying magnetic fields [Soft Matter. 17, 5, 1120-1155]: 1552854-1
\end{itemize}

>>>>

\begin{itemize}
    \item Scalable synthesis of gyroid-inspired freestanding three-dimensional graphene architectures: 1548092-1
    \item Colloidal Jamming at Interfaces: A Route to Fluid-Bicontinuous Gels [Science, 2005, 309, 5744]: 5966820525314
    \item Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, Fibers, and Membranes by Solvent Transfer-Induced Phase Separation (STRIPS): 5913140219015
    \item Magnetophoresis of Magnetic Pickering Emulsions Under Low Field Gradient: Macroscopic and Microscopic 
    Motion [Langmuir 2021, 37, 5, 1811-1822]: "Reprinted (adapted) with permission from 
    Langmuir 2021, 37, 5, 1811-1822. Copyright 2025 American Chemical Society."
    \item Assembling Ellipsoidal Particles at Fluid Interfaces Using Switchable Dipolar Capillary Interactions [Adv. Mater., 26: 6715-6719]: Reproduced under the Creative Commons CC BY License.
    \item Capillary Interactions Between Anisotropic Colloidal Particles, [Phys. Rev. Lett. 2005, 94, 018301]: RNP/25/FEB/088185
    \item State diagram for particle stabilized emulsions. [Soft Matter, 2015,11, 8393-8403]: 1551968-1
    \item Shear dynamics of confined bijels [AIP Advances 1 September 2020; 10 (9): 095304]: Reproduced under the Creative Commons CC BY License.
    \item LB3D: A parallel implementation of the Lattice-Boltzmann method for simulation of interacting amphiphilic fluids [Computer Physics Communications 2017, 217, 149--161]: Reproduced under the Creative Commons CC BY License
\end{itemize}

% \begin{itemize}
%     \item Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, 
%     Fibers, and Membranes by Solvent Transfer‐Induced Phase Separation (STRIPS): 5913140219015
%     \item Scalable synthesis of gyroid-inspired freestanding three-dimensional graphene architectures: 1548092-1
%     \item State diagram for particle stabilized emulsions. [Soft Matter, 2015,11, 8393-8403]: 1551968-1
%     \item Scalable Manufacturing of Hierarchical Biphasic Bicontinuous Structures via Vaporization-Induced 
%     Phase Separation (VIPS) [Materials Letters 2020, 2, 5, 524-530]: "Reprinted (adapted) with permission from 
%     {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
%     \item Modulation of Cellulose Nanocrystals Amphiphilic Properties to Stabilize Oil/Water Interface 
%     [Biomacromolecules 2016, 17, 5, 1748–1756]: "Reprinted (adapted) with permission from 
%     {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
%     \item Dextran-Based Nanoparticles to Formulate pH-Responsive Pickering Emulsions: A Fully Degradable 
%     Vector at a Day Scale [Biomacromolecules 2020, 21, 12, 5358–5368]: "Reprinted (adapted) with permission from 
%     {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
%     \item Stable emulsions with thermally responsive microstructure and rheology using poly(ethylene oxide) star 
%     polymers as emulsifiers [Journal of Colloid and Interface Science, 2013, 394, 284-292]: 5921030909190
%     \item Magnetophoresis of Magnetic Pickering Emulsions Under Low Field Gradient: Macroscopic and Microscopic 
%     Motion [Langmuir 2021, 37, 5, 1811–1822]: "Reprinted (adapted) with permission from 
%     {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
%     \item Influence of magnetic field on the orientation of anisotropic magnetic particles at liquid interfaces 
%     [Phys Chem Chem Phys 2014, 16, 47, 26051-26058]: 1551970-1
%     \item Pickering Emulsions with Controllable Stability [Langmuir, 2005, 21, 6, 2158-2162]: "Reprinted (adapted) with permission from 
%     {COMPLETE REFERENCE CITATION}. Copyright {YEAR} American Chemical Society."
%     \item Bijels Containing Magnetic Particles: A Simulation Study [Langmuir, 2010, 26, 11, 7928-7936]: 
%     "Reprinted (adapted) with permission from {COMPLETE REFERENCE CITATION}. Copyright {YEAR} 
%     American Chemical Society."
%     \item Numerical simulations of particulate suspensions via a discretized Boltzmann equation. Part 2. Numerical results
%     \item Aerobijels: Ultralight Carbon Monoliths from Cocontinuous Emulsions 
%     [Adv. Funct. Mater. 2020, 30, 1908383]: 5921080017718
%     \item Hierarchical assemblies of superparamagnetic colloids in 
%     time-varying magnetic fields [Soft Matter. 17, 5, 1120-1155]: 1552854-1
%     \item Colloidal Jamming at Interfaces: A Route to Fluid-Bicontinuous Gels [Science, 2005, 309, 5744]: 5966820525314
%     \item Capillary Interactions Between Anisotropic Colloidal Particles, [Phys. Rev. Lett. 2005, 94, 018301]: RNP/25/FEB/088185
% \end{itemize}
